\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{longtable}
\usepackage{array}
\setlength{\extrarowheight}{2pt}

\title{Detailed Self-Assessment Questionnaire:\\ Where Are You on the Pyramid of Hate in your location of residence?}
\date{}

\begin{document}
	
	\maketitle
	
	\noindent\textbf{Instructions:} For each statement, mark \fbox{\rule{0pt}{1.5ex}\hspace{1.5em}} for \textbf{Yes} or \fbox{\rule{0pt}{1.5ex}\hspace{1.5em}} for \textbf{No} on the right.
	
	\vspace{1em}
	
	\renewcommand{\arraystretch}{0.75}
	\newcolumntype{L}{>{\raggedright\arraybackslash}p{0.85\textwidth}}
	\newcolumntype{C}{>{\centering\arraybackslash}p{0.20\textwidth}}
	
	\newcounter{qnum}
	\newcommand{\question}[1]{%
		\stepcounter{qnum}\theqnum. #1
	}
	
	\textbf{Level 1: Daily Microaggressions and Bias}
	\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
		\textbf{1A: Biased Attitudes against Jews} & \\[0.5em]
		Has someone told you that: \\ \\
		\question{ "Jews stick together more than other groups"?} & \fbox{Yes} \quad \fbox{No} \\  \\
		
		\question{ "Jews have too much power for such a small group"?} & \fbox{Yes} \quad \fbox{No} \\  \\
		
		\question{ "Jewish mothers are overbearing and controlling"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jewish women are shallow, spoiled, and materialistic"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jewish men are weak, neurotic, and unmanly"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews always find a way into show business and run Hollywood"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews control the news and media"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews are greedy and obsessed with money"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{" Jews are more intelligent and cunning than others"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews secretly control the banks and global economy"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews care more about themselves or Israel than the countries where they live"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews engineer economic crises for their own benefit"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews start wars to make money or gain influence"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews plot to create a one-world government"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews are responsible for killing Jesus"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ "Jews kidnap and murder non-Jewish children for ritual purposes"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		Has someone you know: \\ \\
		
		\question{ avoided discussing issues of antisemitism to keep the conversation “comfortable”?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ refused to acknowledge Jewish holidays or traditions in shared spaces?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ mocked your name because it "sounds Jewish"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ mocked you for using Hebrew words or showing interest in Jewish culture (use of Jewish symbols...), implying it's unnatural or performative?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ made negative comments about Jewish religious customs (e.g., kippah, kosher diet)?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ dismissed antisemitic stereotypes as “just jokes”?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ told you that Jews are “oversensitive” or “brainwashed” when addressing antisemitism?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ expected you to or demanded to know if you justify Israeli policies simply because you are Jewish?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ refused to discuss antisemitism targeting allies, claiming it’s not “real” antisemitism?} & \fbox{Yes} \quad \fbox{No} \\ \\

		\question{ assumed you are wealthy because you are Jewish?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ implied that Jews are “clannish” or “insular”?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{ accused Jews of “playing the victim”?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone you know made assumptions about your intelligence based on your Jewish background?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone you know accused Jews of “stealing jobs” or “taking opportunities”?} & \fbox{Yes} \quad \fbox{No} \\
		
		\end{longtable}
		
		\vspace{0.5em}
		\textbf{1B: Prejudice Based on Expressed or Perceived Opinions}
		\vspace{0.5em}
		
		\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
			
		\question{Has someone questioned your intelligence or judgment for holding favorable views toward Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone dismissed your concerns about antisemitism as exaggerated or as "parroting" Jewish/Israeli narratives?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone suggested you're naive, paid, or manipulated to support Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone interrupted or aggressively challenged you when speaking favorably about Jewish people or Israel, in a way they don't with other topics?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone held you to a different criticism standard regarding Israel than they would other countries?} & \fbox{Yes} \quad \fbox{No} \\ \\
	
		\question{Have you been socially shunned or avoided by others once they learned of your favorable views toward Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone implied that by supporting Israel, you're complicit in global conspiracies?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone accused you of "pinkwashing" or "whitewashing" Israeli actions to silence your supportive voice?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have your motives for supporting Jewish people or Israel been questioned as personal gain or part of a "lobby"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been accused of being part of a powerful Zionist lobby simply for expressing support?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone labeled you with derogatory terms like "Zionist shill" or "self-hating [your identity]"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone implied you're secretly Jewish or have Jewish family to "explain" your stance?} & \fbox{Yes} \quad \fbox{No} \\
		
	\end{longtable}
	\textbf{Level 2: Verbal and Social Exclusion} \\
	\textbf{ 2A: Direct Verbal Harassment and Social Exclusion}
	\vspace{0.5em}
	
	\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
		
		\question{Has someone laughed at, endorsed, or made jokes/negative remarks about Jews, Jewish culture, or those who support Jewish people/Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone shared memes or media \textbf{with you} mocking Jews, Jewish culture, or Israel out of hostility?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone imitated or stereotyped how they imagine a "Zionist" or "Jewish supporter" would speak or act, directing it at you?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone intentionally mispronounced your name, used derogatory nicknames, or refused to use your correct name/pronouns because of your Jewish identity or support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone avoided inviting you to social events because of your Jewish identity?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone avoided sitting near you once they learned you are Jewish?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone avoided you or excluded you from social, professional, or academic events because you are Jewish or support Jewish people/Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been excluded from groups or discussions because your views on Jewish people/Israel were deemed "problematic"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone spread rumors about Jewish religious practices (e.g., blood libel, secret rituals)?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone accused you of "playing the antisemitism card" when you pointed out antisemitic attacks?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone told you to "go (back) to Poland" or that you "don't belong here" because of your identity or views?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone told you that your support for Israel means you "don't care" about other groups or human rights?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone mocked your participation in interfaith events or friendships with Jewish people?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone used slurs or derogatory terms against Jews or allies, even "playfully"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have rumors or misinformation been spread about you (e.g., that you are secretly funded, a spy for Israel)?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have others publicly ostracized you or encouraged others to boycott you/your work due to your support for Jewish people/Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been accused of being a "traitor," "extremist," "fanatic," or "brainwashed" for supporting Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been professionally sidelined or had collaborations ended due to your support for Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone threatened to expose your pro-Jewish/Israel views to your employer or social circles to damage your reputation?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been accused of supporting "apartheid," "genocide," or "Nazism" due to your expressed support for Israel or Jewish people?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone threatened to report your immigration status based on your Jewish background?} & \fbox{Yes} \quad \fbox{No}
	\end{longtable}
	
	\vspace{0.5em}
	\textbf{ 2B: Witnessed Harassment and Institutional Failures}
	\vspace{0.5em}
	
	\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
		
		\question{Have you witnessed coworkers or classmates mimic Jewish accents or mannerisms to mock a Jewish peer?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you overheard a friend or relative justify antisemitic stereotypes (e.g., "Jews are good with money")?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you heard a family member or friend claim that "Jews control the media/government"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone dismissed your achievements or qualifications by attributing them to favoritism because of your Jewish identity or support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone accused you of being "brainwashed" or "indoctrinated" for supporting Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone questioned your mental health or stability for expressing concerns about antisemitism or Israel-related hostility?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been discouraged from speaking about antisemitism or Israel in public or online spaces?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone accused you of using claims of antisemitism to silence criticism of Israel, regardless of your actual intent?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you seen a colleague ostracized at work for defending Israel in discussions?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you witnessed a Jewish peer or colleague excluded or sidelined after disclosing their Jewish identity?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you witnessed a friend being ridiculed for attending a pro-Israel event or Jewish cultural activity?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you witnessed a friend's social-media posts about Israel being flooded with antisemitic comments?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you heard a family member or friend accuse Jews of "exaggerating the Holocaust"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has a colleague or acquaintance dismissed a Jewish person's concerns about antisemitism as "paranoia"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you witnessed coworkers or classmates mock or single out a Jewish student for wearing religious symbols?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you witnessed a teacher, supervisor, or authority figure ignore or dismiss a report of antisemitic bullying by a Jewish person or ally?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you observed digital platforms, class forums, or group chats tolerate antisemitic slurs or propaganda while moderating other forms of hate?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you seen or heard authorities excuse antisemitism as "political disagreement" while punishing milder hate toward other minorities?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you seen someone pressured to denounce Israel or Jewish organizations as a condition for social or professional acceptance?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you observed your institution refuse to investigate repeated complaints of antisemitic harassment despite clear evidence?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have campus or workplace leaders failed to ban or discipline individuals openly celebrating violent attacks on Jews (e.g., rallies praising Hamas)?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you witnessed a supervisor retaliate against a colleague or student for reporting antisemitic hate?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you observed teachers or professors minimize or justify physical attacks on Jewish students as "ordinary conflict"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you seen authorities or HR dismiss antisemitic graffiti or slurs on campus as "free speech" or "harmless vandalism"?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you witnessed a medical, social-service, or legal professional ignore antisemitic abuse reported by a Jewish victim or patient?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
	\end{longtable}

		
	\textbf{Level 3: Discrimination and Institutional Bias} \\ \\[0.5em]
	\textbf{3A. Work and Education Discrimination} \\
	\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
			
		\question{Has a teacher or academic advisor discouraged you from advanced classes due to your Jewish identity or views on Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you faced stricter dress code policies targeting Jewish religious attire?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Were you assigned menial tasks at work despite your qualifications because you are Jewish?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been excluded from professional advancement, such as being overlooked for promotion despite strong performance, because you are Jewish or pro-Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your resume been rejected due to your “Jewish-sounding” name or known affiliations?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been paid less than peers in similar roles after expressing support for Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you experienced unequal access to healthcare, education, or social services because of your Jewish identity?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied mental health or medical care tailored to Jewish needs?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has a healthcare provider dismissed your pain or symptoms as “Jewish exaggeration”?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied participation in extracurricular activities, teams, or clubs because you're Jewish or support Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied the right to display Jewish or Israeli symbols (e.g., menorah, Israeli flag) in shared professional, academic, or cultural spaces?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your request for time off to observe Jewish holidays been consistently denied?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied access to formal networks or career associations because of your Jewish identity or pro-Israel stance?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied opportunities to participate in academic conferences, panels, or research due to your views on Israel or Jewish identity?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied access to leadership roles or membership in organizations due to perceived Jewish/Israel affiliations?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied funding, grants, or institutional support for projects or causes seen as “too favorable to Jews or Israel”?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied a platform to speak or had events cancelled due to pressure from anti-Israel or antisemitic groups?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you experienced a hostile work or academic environment due to anti-Israel or antisemitic rhetoric targeting supporters like you?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been penalized, reprimanded, or punished by your school or employer for defending Israel or speaking against antisemitism?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been subjected to different rules or disciplinary scrutiny compared to others who criticize Israel or Jews?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have your complaints or requests for protection from antisemitic treatment been ignored or dismissed by your workplace or academic institution?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied housing, evicted, or blocked from renting due to your Jewish identity or pro-Israel stance?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\end{longtable}
		
		\vspace{0.8em}
		\textbf{3B. Public Life Discrimination}
		\vspace{0.5em}
		
		\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
		
		\question{Have you been denied or discouraged from membership in a political party or electoral campaign due to being Jewish or perceived Zionist?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you resigned from a position you held in an organization (political party, company, club...) because of persistant antisemitic activity in it?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been excluded from community events or volunteer programs due to your pro-Israel or Jewish stance?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been pressured to publicly disavow Zionism or support for Israel to remain in a position or organization?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been censured or publicly condemned by a group or authority figure for expressing support for Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied access to public spaces or facilities (libraries, arenas, town halls) due to your Jewish identity or advocacy?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your public or nonprofit group been denied recognition due to pro-Israel activities or associations?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your Jewish or pro-Israel center/facility been blocked or delayed in receiving permits/zoning necessary to operate?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you lost sponsorships, contracts, or clients because of your Jewish identity or visible support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been denied protection, assistance, or equal treatment by police, firefighters, or public safety officials due to your Jewish identity or visible support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\end{longtable}
		
		\vspace{0.8em}
		\textbf{3C. Civil and Government Discrimination}
		\vspace{0.5em}
		
		\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
		
		\question{Have you been denied a loan, mortgage, or credit despite good standing due to your Jewish identity?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been excluded from scholarship opportunities or academic programs due to your religion or background as a Jew?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your visa, travel permit, or study abroad application been rejected or stalled due to your support for Israel or your Jewish background?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been required to sign statements disavowing Israel/Zionism to access jobs, student programs, or accommodations?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have your children been excluded, harassed, or treated unfairly at school because of your Jewish identity or views on Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been forced or required to alter your religious appearance (e.g., remove a kippah or Magen David) to comply with workplace or institutional expectations?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your Jewish community or synagogue been excluded from decisions in local governance affecting your neighborhood or space?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you or your community been denied permission to organize a public demonstration, parade, or festival due to perceived pro-Israel/Jewish stance?} & \fbox{Yes} \quad \fbox{No} \\ \\
				
		\question{Has legislation aimed at weakening of denying certain rights for Jews specifically been discussed in legislative bodies?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has legislation aimed at weakening or denying certain rights for Jews specifically been adopted and implemented?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you experienced discriminatory or prejudiced treatment in court (civil or family court) due to your Jewish background or support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have there been calls to register Jews or their supporters as dangerous agents (e.g., “Zionist spies”)?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has the Governnment terminated relations with the State of Israel and espoused hatred of Israel in daily political discourse?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has Government criminalized interactions and/or travels of private citizens with Israel or citizens thereof?}  & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\end{longtable}

		\textbf{Level 4: Antisemitic Violence} \\[0.5em]
		\textbf{4A: Threats and Intimidation} \\ \\
		\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
			
		\question{Have you faced antisemitic harassment in online gaming communities or forums due to your Jewish identity or support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been publicly shamed or ridiculed in a community space (e.g., town hall, school) for expressing concerns about the risk antisemitic violence?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{After reporting antisemitic threats, did authorities or institutions dismiss your concerns as ‘overreactions’ or ‘political opinions’?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has a colleague or employer threatened physical violence against you for advocating against antisemitism in the workplace?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone threatened to destroy your business unless you renounce support for Jewish causes/Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your community / synagogue been subject to threats of attack because of its' association with Jews or perceived support of Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone threatened to “out” your Jewish identity to others without your consent, exposing you to potential risks to your physical wellbeing?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you received threatening phone calls targeting your Jewish identity or support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you received hate mail (physical or electronic) containing antisemitic tropes or violent threats related to your Jewish identity or pro-Jewish/Israel stance?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you received antisemitic deepfake images, audio, or videos intended to discredit or threaten you?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone created fake social media accounts in your name to spread antisemitic content or harass others?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone posted your image or personal details online with calls for harassment or violence because of your Jewish identity or pro-Israel stance?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been intimidated or threatened while attending a public Jewish event (e.g., Hanukkah celebration, Israel solidarity rally)?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been warned by authorities or community members of credible threats against you due to your public support for Jewish people/Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone threatened to falsely accuse you of a crime or misconduct to silence your support for Jewish people/Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone threatened to deport you because of your Jewish background?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been followed or stalked due to your Jewish identity or your pro-Jewish/Israel stance?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you received online death threats or threats of violence specifically linking your support for Jewish people/Israel to the threat?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone threatened to harm your family because you are Jewish or your expressed support for Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your home, car, or property been vandalized with antisemitic symbols or graffiti?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your place of worship (synagogue) been defaced with graffiti or hate messages?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been chased or cornered by a group shouting antisemitic or anti-Israel slurs or threats?} & \fbox{Yes} \quad \fbox{No} \\ \\
		\end{longtable}
		
		\vspace{0.8em}
		\textbf{4B. Physical Violence}
		\vspace{0.5em}
		
		\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
		
		\question{Have you been spat on, shoved, or physically harassed in public because you are Jewish or your expressed support for Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone thrown objects at you or your property (e.g., during a rally) while making antisemitic or anti-Israel remarks?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has someone thrown objects at you from a moving car while shouting antisemitic slurs?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Were your children physically bullied at school for being Jewish or because of your stance in favor of Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you witnessed a friend, family member, or colleague being physically attacked because of their Jewish identity or support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Were you beaten by a group chanting antisemitic or anti-Israel slogans?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Did someone attempt to attack you for wearing Jewish religious attire?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Did someone attempt to hit you with a vehicle or use a weapon against you during a pro-Israel/Jewish event or because you displayed symbols of support?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you survived an attack targeting Jews for their identity?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you survived a violent attack at an event or location associated with Jewish or Israeli support where you were present as an ally?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you or someone close to you been injured in a violent incident (e.g., synagogue shooting, anti-Israel rally) motivated by antisemitism?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Were you denied help (medical etc...) or had help delayed by bystanders or authorities during an attack, because the attack was related to your pro-Israel/Jewish stance?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been hospitalized due to a physical attack motivated by your support for Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Were you sexually assaulted while the perpetrator used antisemitic slurs?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Were you held at gunpoint or threatened with a deadly weapon by someone making clear their motive was your support for Jewish people/Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been targeted with arson or attempted arson against your home, business, or place of worship due to your Jewish identity or support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been forcibly detained, kidnapped, or held against your will because of your Jewish identity or support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\ [0.5em]
		
		\question{Have jewish women or girls been raped in the country you live on account of being Jewish?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have Jews been targeted by murder or assassination attempts for being Jewish or associated with the State of Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\ [0.5em]
		
		\end{longtable}
		
		
		\textbf{Level 5: Systematic Persecution and Genocide} \\[0.5em]
		
		\textbf{ 5A: Systematic Persecution} \\ \\
		\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
		\question{Has an election campaign been run on a platform including hostility toward Jewish people or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Are there state-sponsored or tolerated campaigns to dehumanize Jews or their supporters by portraying them as enemies?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you or your community been subjected to curfews, forced relocation areas, or mobility restrictions based on your Jewish identity or views?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have pro-Jewish or Israel-supportive materials (e.g. books, posters) been confiscated, censored, or destroyed by authorities or organized groups?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has there been public desecration or destruction of Jewish symbols, institutions, or places associated with Jews or Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have Jewish languages (e.g. Hebrew, Yiddish, Ladino...) been banned from educational or public use?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have your religious texts, artifacts, or sacred items been confiscated or destroyed by governmental agents?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Are there coordinated efforts to erase Jewish history, culture, or traditions in your country?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Were your cultural or historical sites, including cemeteries and heritage spaces, looted or intentionally destroyed?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have Jewish schools, charities, or cultural organizations been closed down, merged, or destroyed by decree?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		
		\question{Have you been denied the right to own property or operate businesses due to Jewish identity or support for Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your community experienced sweeping asset seizures, “ethnic tax” policies, or forced economic collapse due to antisemitic legislation?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have Jewish families been stripped of citizenship due to identity-based policies?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has there been mass arrest, exile, or elimination of Jewish religious leaders, academics, or cultural figures?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your Jewish community been forcibly displaced by state forces or organized violence?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have your ancestral burial sites been desecrated by government or law enforcement?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have state threats targeted your children, including family separation unless you renounce pro-Jewish/Israel stances?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Are there laws limiting reproductive rights of Jews or their supporters (e.g. sterilization, population caps)?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have children from your community been forcibly sent to government-run re-education/assimilation facilities?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you or your family been denied access to healthcare, food, water, or schooling due to antisemitic/pro-Israel persecution laws?} & \fbox{Yes} \quad \fbox{No} \\ \\
	
	\end{longtable}
	
	\vspace{0.8em}
	\textbf{5B. Mass Extermination}
	\vspace{0.5em}
	
	\begin{longtable}{>{\raggedright\arraybackslash}p{0.75\textwidth} p{0.2\textwidth}}
	
		\question{Do authorities justify antisemitic killings or genocide as political or national self-defense?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Has your government denied the occurrence of past or ongoing mass killings of Jews?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have senior leaders called for the forced elimination or extermination of Jews or their supporters?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you witnessed modern-day mass killings of Jews in your region?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you received credible threats that place you or other Jewish-linked individuals on execution or extermination lists?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been imprisoned or abducted by mobs, militias, or political entities due to Jewish identity or advocacy?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been tortured or physically mutilated due to your Jewish identity or support for Jewish people/Israel?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been raped or subjected to reproductive violence as an act of antisemitic warfare?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been forced to identify or betray other Jews or Jewish supporters under threat of violence?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you survived or witnessed targeted mass executions of Jewish civilians or pro-Israel groups?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been held inside a ghetto, internment facility, or extermination camp for being Jewish?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Were you forced to take part in watching or destroying Jewish religious/cultural objects under violence or threat?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been subjected to non-consensual medical experimentation based on your Jewish identity?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been forced to dig mass graves or clean execution sites involving Jewish victims?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you lost more than ten members of your family to direct, ideologically driven executions targeting Jews?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been forced to identify your family members' remains from mass graves?} & \fbox{Yes} \quad \fbox{No} \\ \\
		
		\question{Have you been forced to participate in executions or extermination procedures ordered against Jews or Israeli advocates?} & \fbox{Yes} \quad \fbox{No} \\ \\ [0.5em]

	\end{longtable}
	
\end{document}
